Deep Learning

### 2015-01-31 deepreview.tex
edited and inserted Geoff's backprop figures and captions

This rather naive way of performing machine translation has quickly become
competitive with the state-of-the-art and this raises serious doubts about
whether understanding a sentence requires anything like internal symbolic
expressions that are manipulated by binding their symbols to the variables
in judiciously chosen rules of inference.  The encoder-decoder translation
networks do not work by using internal rules of inference in which
variables get bound to symbols. They just use big state vectors, big weight
matrices and scalar non-linearities to get the job done.  Deriving conclusions using only the form of the premises (which is
what formal logic does) is a powerful
technique that people can eventually master, but the translation
results with recurrent nets suggest that it may not be a good model of
the way we normally reason or understand language. Recurrent neural
networks that represent thoughts as big vectors are more compatible with
the view that everyday reasoning involves many simultaneous analogies that
each contribute plausibility to a conclusion~\citep{metaphors,rogers}.

@@

\begin{figure}[htp]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.33\linewidth]{chain-rule.pdf}
\includegraphics[width=0.33\linewidth]{forward-graph.pdf}
\includegraphics[width=0.33\linewidth]{backward-graph.pdf}
}
\caption{
Left: the chain rule of derivatives tells us how
two small effects (that of a small change of $x$ on $y$, and that of $y$ on $z$)
are composed. A small change $\Delta x$ in $x$
gets transformed first into a small change $\Delta y$ in $y$
by getting multiplied by $\frac{\partial y}{\partial x}$
(that is the definition of partial derivative). Similarly,
the change $\Delta y$ creates a change $\Delta z$ in $z$. Substituting one equation
into the other gives the chain rule of derivatives, i.e., how
$\Delta x$ gets turned into $\Delta z$ through multiplication
by the product of $\frac{\partial y}{\partial x}$ and
$\frac{\partial z}{\partial x}$. It also works when $x$, $y$
and $z$ are vectors (and the derivatives are Jacobian matrices). \newline
Middle: many computations, such as the succession of linear and non-linear 
transformations of multi-layer neural networks, can be described as
a graph where each node $i$ computes a quantity $u_i$ (e.g. the
output of an artificial neuron or the value of a parameter such as
a synaptic weight), based on the set of values $a_i$, composed of elements $u_j$ of
predecessors in the graph, i.e., $u_i = f_i(a_i)$. This can be readily
generalized to nodes whose output is a vector or a matrix.\newline
Right: the chain rule can be applied efficiently to computational
flow graphs by recursively computing the derivative of the final
node $u_N$ (e.g., the error to be minimized or the output of the neural network)
with respect to every internal node. The basic recursive equation
is
$\frac{\partial u_N}{\partial u_j} = \sum_{i: j \in a_i} \frac{\partial u_N}{\partial u_i}
\frac{\partial f(a_i)}{\partial u_j}.$
}
\label{fig:backprop-box}
\end{minipage}
}
\end{figure}

>>>>

This rather naive way of performing machine translation has quickly become
competitive with the state-of-the-art and this raises serious doubts about
whether understanding a sentence requires anything like internal symbolic
expressions that are manipulated by binding their symbols to the variables
in judiciously chosen rules of inference.  The encoder-decoder translation
networks do not work by using internal rules of inference in which
variables get bound to symbols. They just use big state vectors, big weight
matrices and scalar non-linearities to get the job done.  Deriving conclusions using only the form of the premises (which is
what formal logic does) is a powerful
technique that people can eventually master, but the translation
results with recurrent nets suggest that it may not be a good model of
the way we normally reason or understand language. Recurrent neural
networks that represent thoughts as big vectors are more compatible with
the view that everyday reasoning involves many simultaneous analogies that
each contribute plausibility to a conclusion~\citep{metaphors,Rogers+McClelland-book2004}.

@@

\begin{figure}[htp]
\fbox{
\begin{minipage}{\textwidth}
\centerline{
\includegraphics[width=0.3\linewidth]{chain-rule.pdf}}
\centerline{
\hspace*{.5mm}\fbox{\includegraphics[width=0.49\linewidth]{bpfig_forward.pdf}}
\hspace*{0mm}\fbox{\includegraphics[width=0.49\linewidth]{bpfig_backward.pdf}}
}
\caption{
{\bf Top.} The chain rule of derivatives tells us how
two small effects (that of a small change of $x$ on $y$, and that of $y$ on $z$)
are composed. A small change $\Delta x$ in $x$
gets transformed first into a small change $\Delta y$ in $y$
by getting multiplied by $\frac{\partial y}{\partial x}$
(that is the definition of partial derivative). Similarly,
the change $\Delta y$ creates a change $\Delta z$ in $z$. Substituting one equation
into the other gives the chain rule of derivatives, i.e., how
$\Delta x$ gets turned into $\Delta z$ through multiplication
by the product of $\frac{\partial y}{\partial x}$ and
$\frac{\partial z}{\partial x}$. It also works when $x$, $y$
and $z$ are vectors (and the derivatives are Jacobian matrices). \newline
{\bf Bottom left.} The equations used for computing the forward pass in a neural net
with two hidden layers. At each layer, we first compute the total input,
$z$, to each unit which is a weighted sum of the outputs of the units in
the layer below. Then a non-linear function $f(.)$ is applied to $z$ to get
the output of the unit.  For simplicity, we have omitted bias terms. \newline
{\bf Bottom right.} The equations used for computing the backward pass. At each hidden
layer we compute the error-derivative w.r.t. the output of each unit which
is a weighted sum of the error-derivatives w.r.t. the total inputs to the
units in the layer above. We then convert the error-derivative w.r.t. the
output into the error-derivative w.r.t. the input by multipling it by the
derivative of $f(z)$.  At the output layer, the error-derivative w.r.t. the
output of a unit is computed by differentiating the cost function. This
gives $y_l-t_l$ If the cost function for unit $l$ is $0.5(y_l-t_l)^2$ where
$t_l$ is the target value.
}
\label{fig:backprop-box}
\end{minipage}
}
\end{figure}
